BSTERGM: Bayesian Separable-Temporal Exponential family Graph Models

### 2020-12-10 doc/doc.tex
tex1211-2

I consider 2 dimentional model as follows.
\[P(Y_t^+=y_t^+|Y_{t-1}=y_{t-1};\theta^+) = \frac{exp((\theta^+)^{T}s(y_t^+, y_{t-1}))}{c(\theta^+, y_{t-1})}\]
\[P(Y_t^-=y_t^-|Y_{t-1}=y_{t-1};\theta^-) = \frac{exp((\theta^-)^{T}s(y_t^-, y_{t-1}))}{c(\theta^-, y_{t-1})}\]
and
\[P(Y_t=y_t|Y_{t-1}=y_{t-1};\theta^+,\theta^-)=P(Y_t^+=y_t^+|Y_{t-1}=y_{t-1};\theta^+) P(Y_t^-=y_t^-|Y_{t-1}=y_{t-1};\theta^-)\]
where
\(s(z_1,z_2)^T=(|z_1|-|z_2|)\)
for $z_1,z_2\in\mathcal{Y}$ with 52 nodes. In other words, the network statistic in the model is
difference of the number of edges for both the formation model and the disolution model.

I use the ordinary normal prior $p(\theta^+)~\mathcal{N}(0,100)$ and $p(\theta^-)~\mathcal{N}(0,100)$,
and set the proposal distribution of main chain $\epsilon~\mathcal{N}(0,0.02)$.
The auxiliary chains consist of 1000 iterations and the main chain consists of 50000 iteration.
After generating the chain, I cut first 10000 samples for a burn-in period and thin the sample by 10.

The posterior estimates for each network and histograms are follows.
%mean, sd
%hist

>>>>

I consider 2 dimentional model as follows.
\[P(Y_t^+=y_t^+|Y_{t-1}=y_{t-1};\theta^+) = \frac{exp((\theta^+)^{T}s(y_t^+, y_{t-1}))}{c(\theta^+, y_{t-1})}\]
\[P(Y_t^-=y_t^-|Y_{t-1}=y_{t-1};\theta^-) = \frac{exp((\theta^-)^{T}s(y_t^-, y_{t-1}))}{c(\theta^-, y_{t-1})}\]
and
\[P(Y_t=y_t|Y_{t-1}=y_{t-1};\theta^+,\theta^-)=P(Y_t^+=y_t^+|Y_{t-1}=y_{t-1};\theta^+) P(Y_t^-=y_t^-|Y_{t-1}=y_{t-1};\theta^-)\]
where
\(s(z_1,z_2)^T=(|z_1|-|z_2|)\)
for $z_1,z_2\in\mathcal{Y}$ with 52 nodes. In other words, the network statistic in the model is
difference of the number of edges for both the formation model and the dissolution model.

I use the ordinary normal prior $p(\theta^+)\sim\mathcal{N}(0,100)$ and $p(\theta^-)\sim\mathcal{N}(0,100)$,
and set the proposal distribution of main chain $\epsilon\sim\mathcal{N}(0,0.0004)$.
The auxiliary chains consist of 1000 iterations and the main chain consists of 50000 iteration.
In this setting, the BSTERGM fitting algorithm run 250 iteration of main chain per a minute on the intel i7-8700(3.20GHz) CPU.

After generating the chain, I cut first 10000 samples for a burn-in period and thin the sample by 10.
The posterior estimates for each network and histograms are follows.
%mean, sd
%hist
